Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-05-07 Phase_II/draft/main.tex
authors

>>>>

\author[Rai et al.]{Km Nitu Rai,$^{1,2}$ Yuri van der Burg,$^{3}$ Soumen Basak,$^{1}$ Prasenjit Saha,$^{3}$ and
	Subrata Sarangi$^{4}$ \\ \\
	$^{1}$School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO,
	Vithura,\\ Thiruvananthapuram 695551, Kerala, India \\
	$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India. \\
	$^{3}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland \\
	$^{4}$School of Applied Sciences, Centurion University of Technology and Management, Odisha-752050, India.}
